---
title: "Dead Dogs Analytics - YouTube Analysis using tuber"
author: "Alessandro Speranza"
date: "10/28/2020"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cash = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(purrr)
library(tuber)
```
Tuber package works using YouTube Data API, not the Analytics and Reporting APIs


## YouTube Authentication

```{r}
client_id <- "311472921616-i4e4lhb60sdn18i0tvbjcsveppevcju4.apps.googleusercontent.com"
client_secret <- "ynWLz2HYInU3u92YYFKOovIT"

# Use the youtube oauth 
yt_oauth(app_id = client_id,
         app_secret = client_secret,
         token = '')
```

## Channel

### Source: Storybench - How to download YouTube data in R using “tuber” and “purrr”
https://www.storybench.org/how-to-download-youtube-data-in-r-using-tuber-and-purrr/

```{r}
alessandro_speranza_channel_id <- stringr::str_split(
    string = "https://www.youtube.com/channel/UC6CV_32l8omBfcliOOQnIew", 
    pattern = "/", 
    n = 5,
    simplify = TRUE)[ , 5]

# Get channel statistics
chstat <-  tuber::get_channel_stats("UC6CV_32l8omBfcliOOQnIew")

# Transform list to tibble
chstat_df <- purrr::map_df(chstat[["snippet"]][["title"]], unlist) %>% 
  janitor::clean_names()

chstat_df2 <- purrr::map_df(chstat[["statistics"]], unlist) %>% 
  janitor::clean_names()
```


## Playlists

```{r}
playlists <- tuber::get_playlists(filter = c(channel_id = "UC6CV_32l8omBfcliOOQnIew"))

# Transform list to tibble
playlists_df <- purrr::map_df(playlists[["items"]], unlist) %>% 
  janitor::clean_names()

# or
df <- as_tibble(do.call(cbind, playlists))
df2 <- map_df(df$items, unlist)
```

## Playlist Items

```{r}
rehearsals_playlist <- get_playlist_items(filter = c(playlist_id = "PLhIw1_0YGPER3H3lpApMLkc2d676B-lpD"), part = "contentDetails")

# Create a vector with all the video IDs
rehearsals_video_ids <- rehearsals_playlist %>% 
  select (contentDetails.videoId) %>% 
  dplyr::pull()

# Get stats and convert results to data frame
rehearsals_video_all_stats <- purrr::map_df(rehearsals_video_ids, tuber::get_stats)
```

## Videos

```{r}
# Get Statistics of a Video
video_stats <- get_stats(video_id = "ZZp_kf68x3o")

video_stats_df <- purrr::map_df(video_stats, unlist) %>% 
  janitor::clean_names()


# Get Information About a Video
video_details <- get_video_details(video_id = "ZZp_kf68x3o", part = "fileDetails")

videos <- list_channel_videos(channel_id ="UC6CV_32l8omBfcliOOQnIew",  max_results = 100)
```

## Get statistics of all the videos in a channel - Attempt 1
```{r}
a <- list_channel_resources(filter = c(channel_id = "UC6CV_32l8omBfcliOOQnIew"), part="contentDetails")

# Uploaded playlists:
playlist_id <- a$items[[1]]$contentDetails$relatedPlaylists$uploads

# Get videos on the playlist
vids <- get_playlist_items(filter= c(playlist_id=playlist_id), max_results = 100) 

# Video ids
vid_ids <- as.vector(vids$contentDetails.videoId)

# Function to scrape stats for all vids
get_all_stats <- function(id) {
  get_stats(id)
} 

# Get stats and convert results to data frame 
res <- map_df(vid_ids, get_all_stats)
```


## Get statistics of all the videos in a channel - Attempt 2 -->>> FUNZIONA!!!

<https://www.rdocumentation.org/packages/tuber/versions/0.9.2/topics/get_stats>

```{r}
get_all_videos <- function(channelID) {
  start <- Sys.time()
  a <- list_channel_resources(filter = c(channel_id = channelID), part="contentDetails")

  playlist_id <- a$items[[1]]$contentDetails$relatedPlaylists$uploads

  vids <- get_playlist_items(filter= c(playlist_id=playlist_id), max_results = 100) 

  vid_ids <- as.vector(vids$contentDetails.videoId)

  get_all_stats <- function(id) {
    get_stats(id)
  } 

  res <- lapply(vid_ids, get_all_stats)
  details <- lapply(vid_ids, get_video_details)
  res_df <- do.call(what = bind_rows, lapply(res, data.frame))

  details_tot <- data.frame(id = NA, title = NA, date = NA)

  for (p in 1:length(details)) {
    id <- details[[p]]$items[[1]]$id
    Title <- details[[p]]$items[[1]]$snippet$title
    Publish_date <- details[[p]]$items[[1]]$snippet$publishedAt

    detail <- data_frame(id = id, titulo = Title, Fechasubida = Publish_date)
    details_tot <- rbind(detail, details_tot)
  }

  res_df$url <- paste0("https://www.youtube.com/watch?v=", res_df$id)

  res_df <<- merge(details_tot, res_df, by = "id")

  end <- Sys.time()
  diff <- end - start
  print(diff)
}
```

get_all_videos("UC6CV_32l8omBfcliOOQnIew")

```{r}
a <- list_channel_resources(filter = c(channel_id = "UC6CV_32l8omBfcliOOQnIew"), part="contentDetails")

  playlist_id <- a$items[[1]]$contentDetails$relatedPlaylists$uploads

  vids <- get_playlist_items(filter= c(playlist_id=playlist_id), max_results = 100) 

  vid_ids <- as.vector(vids$contentDetails.videoId)
  
 res <- lapply("WiSUKa4LSP4", get_all_stats)
  details <- lapply("WiSUKa4LSP4", get_video_details) # --> qui nello snippet mi trova il nome del video, descrizioni, etc
  res_df <- do.call(what = bind_rows, lapply(res, data.frame))
```



