---
title: "Calling YouTube Data API Combined - Dead Dogs Analytics Project"
author: "Alessandro Speranza"
date: "01/20/2021"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cash = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(plotly) # BE CAREFUL!! load plotly pkg before httr pkg
library(janitor)
library(jsonlite)
library(httr)
library(here)
```

# Google Authentication

```{r}
endpoints <- oauth_endpoints("google")

# IMPORTANT! Connect to Google with Alessandro Speranza account
myapp <- oauth_app("dead-dogs-analytics-311702",
                   key = "930372143435-m3db5ec7dl300guvbu5i3o5khk6g6fpe.apps.googleusercontent.com",
                   secret = "BijkxeCom14MlLYtW-vfofEh")

access_token <- oauth2.0_token(endpoints, myapp, scope = "https://www.googleapis.com/auth/yt-analytics.readonly")
```

# get_channel info using YouTube Data API - Real time Data

```{r}
api_call_channel <- "https://www.googleapis.com/youtube/v3/channels?key=AIzaSyCviXCt3rQPfDaNvuFIaWCE24gNx7q0Dfs&id=UC6CV_32l8omBfcliOOQnIew&part=snippet,contentDetails,statistics&maxResults=15"

api_result_channel <- httr::GET(api_call_channel)

json_result_channel <- httr::content(api_result_channel, "text", encoding="UTF-8")

# Process the raw data into a data frame
json_channel <- fromJSON(json_result_channel, flatten = T)

channels <- as.data.frame(json_channel) %>% 
   janitor::clean_names()
```

# get_playlists info using YouTube Data API - Real time Data

```{r}
api_call_playlists <- "https://www.googleapis.com/youtube/v3/playlists?key=AIzaSyCviXCt3rQPfDaNvuFIaWCE24gNx7q0Dfs&channelId=UC6CV_32l8omBfcliOOQnIew&part=snippet,contentDetails,player,status&maxResults=15"

api_result_playlists <- httr::GET(api_call_playlists)

json_result_playlists <- httr::content(api_result_playlists, "text", encoding="UTF-8")

# Process the raw data into a data frame
json_playlists <- fromJSON(json_result_playlists, flatten = T)

playlists <- as.data.frame(json_playlists) %>% 
   janitor::clean_names() %>%
   rename(playlist_id = items_id,
          playlist_published_date = items_snippet_published_at,
          channel_id = items_snippet_channel_id,
          playlist_title = items_snippet_title,
          playlist_description = items_snippet_description,
          channel_title = items_snippet_channel_title,
          playlist_status = items_status_privacy_status,
          playlist_videos_count = items_content_details_item_count,
          playlist_embed_html = items_player_embed_html
          ) %>% 
   select(playlist_id,
          playlist_title,
          playlist_description,
          playlist_published_date,
          playlist_status,
          playlist_videos_count,
          channel_id,
          channel_title,
          playlist_embed_html)

playlists_vector <- playlists %>%
   select (playlist_id) %>%
   dplyr::pull()
```

# Get all the items in all the playlists of a channel - Real time Data

```{r}
get_all_playlist_items <- function(playlist_id) {
  
api_call_playlistItems <- str_c("https://www.googleapis.com/youtube/v3/playlistItems?key=AIzaSyCviXCt3rQPfDaNvuFIaWCE24gNx7q0Dfs&playlistId=", playlist_id,"&part=snippet,status&maxResults=50")
  
api_result_playlistItems <- httr::GET(api_call_playlistItems)

json_result_playlistItems <- httr::content(api_result_playlistItems, "text", encoding="UTF-8")

# Process the raw data into a data frame
json_playlistItems <- fromJSON(json_result_playlistItems, flatten = T)

playlistItems <- as.data.frame(json_playlistItems) %>%
  janitor::clean_names()
  
}

all_playlist_items <- purrr::map_df(playlists_vector, get_all_playlist_items) %>% 
  rename(playlist_id = items_snippet_playlist_id,
         video_id = items_snippet_resource_id_video_id,
         video_title = items_snippet_title,
         video_description = items_snippet_description,
         video_published_date = items_snippet_published_at,
         video_status = items_status_privacy_status,
         playlist_video_position = items_snippet_position,
         playlist_total_videos = page_info_total_results,
         channel_id = items_snippet_channel_id,
         channel_title = items_snippet_channel_title) %>% 
  select(video_id,
         video_title,
         video_description,
         video_published_date,
         video_status,
         playlist_id,
         playlist_video_position,
         playlist_total_videos,
         channel_id,
         channel_title)

all_video_ids_vector <- all_playlist_items %>% 
  select (video_id) %>%
   dplyr::pull()
```

# Get all the videos stats - Real time Data

```{r}
get_all_videos_info <- function(video_id) {
  
api_call_videos <- str_c("https://www.googleapis.com/youtube/v3/videos?key=AIzaSyCviXCt3rQPfDaNvuFIaWCE24gNx7q0Dfs&id=", video_id, "&part=statistics&maxResults=50")

api_result_videos <- httr::GET(api_call_videos)

json_result_videos <- httr::content(api_result_videos, "text", encoding="UTF-8")

# Process the raw data into a data frame
json_videos <- fromJSON(json_result_videos, flatten = T)

videos <- as.data.frame(json_videos) %>% 
   janitor::clean_names()  
  
}

all_videos_stats <- map_df(all_video_ids_vector, get_all_videos_info) %>% 
  mutate(items_statistics_view_count = as.integer(items_statistics_view_count),
         items_statistics_like_count = as.integer(items_statistics_like_count),
         items_statistics_dislike_count = as.integer(items_statistics_dislike_count),
         items_statistics_favorite_count = as.integer(items_statistics_favorite_count),
         items_statistics_comment_count = as.integer(items_statistics_comment_count)) %>%
  rename(video_id = items_id,
         views = items_statistics_view_count,
         likes = items_statistics_like_count,
         dislikes = items_statistics_dislike_count,
         favorites = items_statistics_favorite_count,
         comments = items_statistics_comment_count) %>% 
  select(video_id, 
         views, 
         likes, 
         dislikes, 
         favorites,
         comments)
```

# Join playlist info & video stats - Real time Data

```{r}
playlists_videos <- playlists %>%
  inner_join(all_playlist_items, by = "playlist_id") %>%  
  inner_join(all_videos_stats, by = "video_id") %>%
  mutate(video_published_date = as.Date(video_published_date), 
            video_total_views = views,
            video_total_likes = likes,
            video_total_dislikes = dislikes,
            channel_id = channel_id.x,
            channel_title = channel_title.x) %>%
  select(video_id,
         video_title,
         video_description,
         video_published_date,
         video_total_views, 
         video_total_likes, 
         video_total_dislikes,
         playlist_id,
         playlist_title,
         channel_id,
         channel_title
         ) %>%
  arrange(desc(video_total_views))

# glimpse(playlists_videos)
```

# Creating the TOP 10 rank
```{r}
top10_rank <- playlists_videos %>% 
  slice_max(video_total_views, n = 10) %>% 
  select(video_title, video_total_views) %>% 
  tidyr::separate(video_title, sep = "-", into = c("song", "concert"), remove = FALSE) %>% 
  mutate(song = stringr::str_trim(song), 
         concert = stringr::str_trim(concert),
         video_title_plot = str_c(song, concert, sep = "\n")) %>% 
  dplyr::relocate(video_title_plot, .before = video_total_views)

saveRDS(top10_rank, file = "data/top10_rank.rds")
```

# Creating the TOP 10 rank - Alternative method using factors with forcats
```{r}
top10_rank_fct <- playlists_videos %>%
  select(video_title, video_total_views) %>% 
  tidyr::separate(video_title, sep = "-", into = c("song", "concert"), remove = FALSE) %>% 
  dplyr::mutate(song = stringr::str_trim(song), 
         concert = stringr::str_trim(concert),
         video_title_plot = str_c(song, concert, sep = "\n"),
         video_title_fct_plot = forcats::fct_lump_n(video_title_plot, n = 10, w = video_total_views, other_level = "Remaining Songs"),
         ) %>% 
  group_by(video_title_fct_plot) %>% 
  summarise(video_total_views = sum(video_total_views)) %>%
  arrange(desc(video_total_views)) %>% 
  dplyr::mutate(position = dplyr::case_when(video_title_fct_plot == "Remaining Songs" ~ 11,
                                     TRUE ~ (dplyr::row_number() - 1)),
                video_title_fct_plot = forcats::fct_rev(forcats::fct_reorder(video_title_fct_plot, position)))
  
levels(top10_rank_fct$video_title_fct_plot)


pal <- c("goldenrod1",
         rep("#1F4364", length(top10_rank_fct$video_title_fct_plot)))

ggplot(top10_rank_fct, aes(x = video_total_views, y = video_title_fct_plot, fill = video_title_fct_plot)) +
  geom_col() +
  scale_fill_manual(values = pal, guide = "none") +
  theme_minimal()

# vedere come colorare le barre per playlists



sum(top10_rank_fct$video_total_views)



saveRDS(top10_rank_fct, file = "data/top10_rank_fct.rds")
```

#7 Lollipop with absolute values

```{r}
top10_rank2 <- top10_rank %>% 
  mutate(x2 = fct_reorder(video_title_plot, video_total_views))

saveRDS(top10_rank2, file = "data/top10_rank2.rds")

ggplot(top10_rank2, aes(x = video_title_plot, y = video_total_views)) + 
   geom_segment(aes(x=x2, xend=x2,y=0,yend=video_total_views), color = "#1380A1", size = 4, alpha = .6) +
   geom_point(color = "#1380A1", size = 6) +
    geom_text(aes(label = video_total_views, size = 2, hjust = -0.5)) +
   coord_flip() +
  # Layout Tuning
  # bbc_style() +
  theme_ipsum_rc() +
  scale_color_ipsum() +
  ggtitle("Dead Dogs Songs - Top 10") +
  xlab("") +
  ylab("views")
  # theme(plot.title = element_text(color="red", size=14, face="bold.italic", hjust = -1.5),
        # axis.title.x = element_text(colour = "blue"))
```

# Get all the videos stats - Historical Data

```{r}
get_all_videos_hist_info <- function(video_id) {
  
request <- str_c("https://youtubeanalytics.googleapis.com/v2/reports?dimensions=day,video&metrics=views&filters=video==", video_id, "&sort=-day&startDate=2016-01-01&endDate=2099-12-31&ids=channel==MINE")

req_youtube <- GET(request, config(token = access_token))

youtube_text <- content(req_youtube, "text", encoding="UTF-8")

youtube_json <- fromJSON(youtube_text, flatten = TRUE)

videos_hist <- as.data.frame(youtube_json[["rows"]]) %>% 
  arrange(V1) %>%
  transmute(views_date = as.Date(V1),
            video_id = V2,
            video_daily_views = as.numeric(V3)) %>%
  complete(views_date = seq.Date(min(views_date), lubridate::today(), by = "day")) %>%
  fill(video_id) %>%
  mutate(video_daily_views = ifelse(is.na(video_daily_views), 0, video_daily_views))
  
}

all_videos_stats_hist <- map_df(all_video_ids_vector, get_all_videos_hist_info)
```


# Join playlist info & video hist stats - Historical Data
```{r}
playlists_videos_hist <- inner_join(all_videos_stats_hist, playlists_videos, by = "video_id")
```

# Adding cumulative views - Historical Data
```{r}
playlists_videos_hist_cum <- playlists_videos_hist %>%
  filter(video_id %in% c("YyS7cqFRUvI","29laglX3M1g")) %>%
  group_by(video_id) %>% 
  mutate(video_cum_views = cumsum(video_daily_views)) %>% 
  relocate(video_cum_views, .after = video_daily_views) %T>% # magrittr special pipe
  saveRDS(file = "data/playlists_videos_hist_cum.rds")
```